### 2015-04-09 thesis/thesis/cover.tex
initial changes

\cutitle{Modeling and Verifying Probabilistic Social Commitments in Multi-Agent Systems}

\cudept{Computer Science and Software Engineering}   % your dept.
\cudegree{Doctor of Philosophy}           % your expected degree <-,
\cudegreeshort{Ph.~D.}
\culname{Sultan}                    % your family name
\cufname{Khalid Ibrahim}                    % your given name

\cusupervisor{Dr. Jamal Bentahar}        % your Big-Boss complete name
%\cucosupervisor{Dr. }   % your small big-boss name
\cuexaminerA{Dr. Olga Ormandjieva}
\cuexaminerB{Dr. Rachida Dssouli}
\cuexaminerC{Dr. Abdessamad Ben Hamza}
%\cuexaminerA{}
\cuextexaminer{Dr. Elhadi Shakshuki}     % Another of the previous kind

@@

\cumonth{January}                % the month you expected to graduate
\cuyear{2015}                 % and the year.
%\cudedication{\ \\ \\ \\ \\ \\ \\ \\ \\
%\begin{center}{\bf{To My Parents,\\ My Wife and daughter,\\ and My Brothers and Sisters.}} \\
%\end{center}}
\cuabstract{\input{abstract}}
%%
%
%
%
\cuthanks{\input{ack}}

>>>>

\cutitle{Efficient Community Formation for Web Services}

\cudept{Computer Science and Software Engineering}   % your dept.
\cudegree{Doctor of Philosophy}           % your expected degree <-,
\cudegreeshort{Ph.~D.}
\culname{Khosrowshahi-Asl}                    % your family name
\cufname{Ehsan}                    % your given name

\cusupervisor{Dr. Jamal Bentahar}        % your Big-Boss complete name
\cucosupervisor{Dr. Hadi Otrok}   % your small big-boss name
\cuexaminerA{Dr. O}
\cuexaminerB{Dr. R}
\cuexaminerC{Dr. A}
%\cuexaminerA{}
\cuextexaminer{Dr. E}     % Another of the previous kind

@@

\cumonth{July}                % the month you expected to graduate
\cuyear{2015}                 % and the year.
%\cudedication{\ \\ \\ \\ \\ \\ \\ \\ \\
%\begin{center}{\bf{To My Parents,\\ My Wife and daughter,\\ and My Brothers and Sisters.}} \\
%\end{center}}
\cuabstract{\input{abstract}}
%%
%
%
%
\cuthanks{\input{ack}}
